A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-01-25 paper/draft.tex
generate pooled map of partisanship brazil

First, that the distribution of partisan affiliation varies significantly over the national territory, with its predominance in the Northeast, as well as in the Northern regions of the country. The Midwest and Southeast appear to have the lowest prevalence of partisan affiliation. Second, that there is wide variation with respect to the prevalence of partisanship. In particular, some municipalities are almost entirely occupied by party members, with over 60 percent of its workforce affiliated to some party.

\begin{figure}
    \includegraphics{figures/maps/pooled.png}
    \caption{\textbf{Proportion of party-affiliated members by municipality (2015)}. Darker colors indicate a larger degree of partisan affiliation. This visualization includes all bureaucrats, from high-level managers to service staff.}
    \label{fig:map_pooled}
\end{figure}

>>>>

First, that the distribution of partisan affiliation varies significantly over the national territory, with its predominance in the Northeast, as well as in the Northern regions of the country. The Midwest and Southeast appear to have the lowest prevalence of partisan affiliation. Second, that there is wide variation with respect to the prevalence of partisanship. In particular, some municipalities are almost entirely occupied by party members, with over 60 percent of its workforce affiliated to a party. Others are largely autonomous from party members, with less than 10 percent of municipal workers affiliated to a party.

\begin{figure}[H]
    \centering
    \includegraphics{figures/maps/pooled.png}
    \caption{\textbf{Proportion of party-affiliated members by municipality (2015)}. Darker colors indicate a larger degree of partisan affiliation. This visualization includes all bureaucrats, from high-level managers to service staff.}
    \label{fig:map_pooled}
\end{figure}
